Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-23 tex/v3/appendix.tex
update suppl
update
modif in appendix

\paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.

@@

lemma expresses a lower and upper bounds with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 

>>>>

Next, we bound the two terms $\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty.$
% \paragraph{Bounds of}$\norm{{u}^{\textrm{sc}} - {u}^\star}_\infty $ and $\norm{{v}^{\text{sc}} - {v}^\star}_\infty $.

@@

lemma expresses an upper bound with respect to $\ell_1$-norm of $\mu^{\text{sc}}$and $\nu^{\text{sc}}$. 
